### 2023-01-18 paper.tex
Feedback for Section VIII

	Blockchain technologies are a growing industry and research field. With the introduction of smart contracts on second generation blockchains, the scope of application of blockchains has increased, as has corresponding gas costs and consequently, energy consumption. The immutable nature of a blockchain is what makes it secure, but that also means that developers have to write efficient and bug-free code before deploying smart contracts. Hence, tools for developers to optimize and check their code, are under active research. The repository introduced in this paper aims to aid such researchers by helping them to understand and analyze the effects of specific changes of the source code on the outcomes of the smart contract, especially in automating and finding new ways to optimize gas costs. In spite of the mentioned limitations, the repository offers to provide researchers with complete information about a smart contract and its versions.

	As has already been mentioned before the script, and consequently the repository, can be extended to include source files using other smart contract programming languages. Also, a compiler can be included as part of the script in order to generate and store the bytecode of the collected contracts. The source of data in the repository can be expanded, crawling other public repositories, or even private repositories a user may have access to. An attempt can be made to reconstruct the version history of a source file across multiple branches of the repository, to enable more fine-grained analysis. A gas-cost estimation framework, such as GASOL \cite{gasol} can be integrated into the script to generate gas cost estimations of the collected contract versions. Finally, the repository can be associated with a Web app that can make it easier to visualize the repository of contracts and also provide APIs for more nuanced filtering and retrieval of the dataset, even without knowledge of SQL. These tools can also be included as a plugin to an IDE that can enable easier interaction with the database.

	Apart from the improvements to the repository itself, the next steps involve actually using the repository for applying code mining algorithms, as intended. Upcoming research using this repository should aim at using the enhanced information in this repository towards achieving the research aims mentioned in the previous sections, primarily in the fields of gas consumption, machine learning and qualitative and quantitative analysis of the smart contracts.
	\bibliographystyle{IEEEtran}
	\bibliography{biblio}

>>>>

	Blockchain technologies are a growing industry and research field. With the introduction of smart contracts on second generation blockchains, the scope of application of blockchains has increased, as has corresponding gas costs and consequently, energy consumption. The immutable nature of a blockchain is what makes it secure, but that also means that developers have to write efficient and bug-free code before deploying smart contracts. Hence, tools for developers to optimize and check their code, are under active research. The Smart Contract Repository introduced in this paper aims to aid such researchers by helping them to understand and analyze the effects of specific changes of the source code on the outcomes of the smart contract, especially in automating and finding new ways to optimize gas costs. In spite of the mentioned limitations, the repository offers to provide researchers with complete information about a smart contract and its versions.

	As has already been mentioned before, the script, and consequently the repository, could be extended to include source files using other smart contract programming languages. Also, a compiler could be included as part of the script in order to generate and store the bytecode of the collected contracts. The source of data in the repository could be expanded, crawling other public repositories, or even private repositories a user may have access to. An attempt could be made to reconstruct the version history of a source file across multiple branches of the repository, to enable more fine-grained analysis. A gas-cost estimation framework, such as GASOL \cite{gasol} could be integrated into the script to generate gas cost estimations of the collected contract versions. Finally, the repository could be associated with a Web app that can make it easier to visualize the repository of contracts and also provide APIs for more nuanced filtering and retrieval of the dataset, even without knowledge of SQL. These tools could also be included as a plugin to an IDE that can enable easier interaction with the database.

	Apart from the improvements to the repository itself, the next steps involve actually using the repository for applying code mining algorithms, as intended. Upcoming research using this repository should aim at using the enhanced information in the Smart Contract Repository towards achieving the research aims mentioned in this paper---primarily in the fields of gas consumption, machine learning and qualitative and quantitative analysis of the smart contracts.
	\bibliographystyle{IEEEtran}
	\bibliography{biblio}
